Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-09-30 exp1/present2013.tex
Comment out some stuff
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@644 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass[english,aspectratio=169]]{ifislide}
\documentclass[english,print,aspectratio=169]{ifislide}
%\documentclass[english,handout,aspectratio=169]{ifislide}

\usepackage[utf8]{inputenc}
% Packages used specific for this lecture:
\usepackage{tikz}
%\usepackage{bussproofs}
%\usepackage{textpos}

\EnableBpAbbreviations

\usetikzlibrary{arrows,shapes,mindmap}
\usetikzlibrary{decorations.pathmorphing}
\tikzstyle{resource}=[ellipse,draw=black!40,fill=blue!20,thick, font=\ttfamily]
\tikzstyle{blank}=[ellipse,draw=black!40,fill=white!40,thick, font=\ttfamily]
\tikzstyle{literal}=[rectangle,text centered,draw=black!40,fill=black!20,thick]
\tikzstyle{predicate}=[sloped,above,text centered,midway,font={\scriptsize\ttfamily}]
\tikzstyle{predicateb}=[left,midway,font={\scriptsize\ttfamily}]
\tikzstyle{class}=[rectangle,text centered,draw=black!40,fill=white,thick]
\usetikzlibrary{arrows,automata}

@@

\IfiTOCSlide       % inserts today's plan frame

>>>>

%\documentclass[english,aspectratio=169]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
\documentclass[english,handout,aspectratio=169]{ifislide}

\usepackage[utf8]{inputenc}
% Packages used specific for this lecture:

%\usepackage{bussproofs}
%\usepackage{textpos}

%\EnableBpAbbreviations
%% \usepackage{tikz}

%% \usetikzlibrary{arrows,shapes,mindmap}
%% \usetikzlibrary{decorations.pathmorphing}
%% \tikzstyle{resource}=[ellipse,draw=black!40,fill=blue!20,thick, font=\ttfamily]
%% \tikzstyle{blank}=[ellipse,draw=black!40,fill=white!40,thick, font=\ttfamily]
%% \tikzstyle{literal}=[rectangle,text centered,draw=black!40,fill=black!20,thick]
%% \tikzstyle{predicate}=[sloped,above,text centered,midway,font={\scriptsize\ttfamily}]
%% \tikzstyle{predicateb}=[left,midway,font={\scriptsize\ttfamily}]
%% \tikzstyle{class}=[rectangle,text centered,draw=black!40,fill=white,thick]
%% \usetikzlibrary{arrows,automata}

@@

%\IfiTOCSlide       % inserts today's plan frame
